### 2020-08-24 3_implementation.tex
Apply Alex's comments.

Task-based systems include OmpSs~\cite{OmpSs11}, OpenMP
4.0~\cite{OpenMPSpec40}, PaRSEC~\cite{PARSEC13, PARSEC_DTD},
Realm~\cite{Realm14}, Regent~\cite{Regent15}, and
StarPU~\cite{StarPU11}. Though the details vary, these systems
typically provide implicit parallelism, where tasks are enumerated
sequentially (in program order) and the dependencies between tasks are
analyzed automatically to construct a \emph{dependence graph} that
guides the execution of tasks. PaRSEC provides two modes,
\emph{dynamic task discovery} (DTD)~\cite{PARSEC_DTD}, which operates
as above, and \emph{parameterized task graphs} (PTG)~\cite{PARSEC13},
where the dependence graph is constructed automatically from an
analytical representation of the task graph. Realm (unlike the others
above) is explicitly parallel and requires tasks to be connected
explicitly via \emph{events}. StarPU, in addition to its usual,
implicitly parallel mode, also provides a mode where MPI is used for
synchronization (and is thus explicitly parallel).

Among distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to manually prune the task graph, skipping tasks not
mapped for execution onto a given node, plus a ``halo'' consisting of
tasks connected via dependencies to the set of node-local tasks. Because the dynamic
checks to see if a task should be executed are not free of cost, we
also provide versions of the PaRSEC and StarPU implementations
(labeled \lstinline{shard} and \lstinline{expl}, respectively)
hand-written to minimize such costs. PaRSEC \lstinline{shard} uses the
DTD mode but manually minimizes dynamic checks. StarPU
\lstinline{expl} uses the MPI integration described above. We see in
Section~\ref{subsec:scalability} that such modifications are needed to
achieve optimal scalability. Regent performs an equivalent
optimization at compile time~\cite{ControlReplication17} that does not
require user intervention and preserves the original, implicitly
parallel programming model of the language.

>>>>

Task-based systems include OmpSs~\cite{OmpSs11}, OpenMP
4.0~\cite{OpenMPSpec40}, PaRSEC~\cite{PARSEC13, PARSEC_DTD},
Realm~\cite{Realm14}, Regent~\cite{Regent15}, and
StarPU~\cite{StarPU11}. Though the details vary, these systems
typically provide implicit parallelism, where tasks are enumerated
sequentially (in program order) and the dependencies between tasks are
analyzed automatically to construct a \emph{dependence graph} that
guides the execution of tasks. PaRSEC provides two modes,
\emph{dynamic task discovery} (DTD)~\cite{PARSEC_DTD}, which operates
as above, and \emph{parameterized task graphs} (PTG)~\cite{PARSEC13},
where the dependence graph is constructed automatically from an
analytical representation of the task graph. Realm (unlike the others
above) is explicitly parallel and requires tasks to be connected
explicitly via \emph{events}. Realm is the low-level execution engine for Regent and thus serves as a limit study of what can be achieved with Regent. StarPU, in addition to its usual,
implicitly parallel mode, also provides a mode where MPI is used for
synchronization (and is thus explicitly parallel).

Among implicitly parallel, distributed task-based systems, there can be a scalability
bottleneck due to enumerating tasks sequentially. PaRSEC and StarPU
allow users to manually prune the task graph, skipping tasks not
mapped for execution onto a given node, plus a ``halo'' consisting of
tasks connected via dependencies to the set of node-local tasks. Because the dynamic
checks to see if a task should be executed are not free of cost, we
also provide versions of the PaRSEC and StarPU implementations
(labeled \lstinline{shard} and \lstinline{expl}, respectively)
hand-written to minimize such costs. PaRSEC \lstinline{shard} uses the
DTD mode but manually minimizes dynamic checks. StarPU
\lstinline{expl} uses the MPI integration described above. We see in
Section~\ref{subsec:scalability} that such modifications are needed to
achieve optimal scalability. Regent performs an equivalent
optimization at compile time~\cite{ControlReplication17} that does not
require user intervention and preserves the original, implicitly
parallel programming model of the language.

### 2020-08-24 5_evaluation.tex
minor edit to say parsec also support both inline and offline configurations
Apply Alex's comments.

One question when considering different programming
systems is: How much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, Realm, and Regent,
support both configurations.

@@

We observe that overheads vary by over 5 orders of
magnitude. The most efficient systems are explicitly parallel
and provide very lightweight mechanisms for parallelism. Task-based systems for HPC tend to be next most efficient, and
provide additional features such as automatic dependency discovery and
data movement. Slower systems tend to be designed primarily for
large-scale data analysis or workflows. It is worth
remembering that these are \emph{minimum}
effective task granularities. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively.
Notably, the ideal-limit intersection (black circle) requires only a
run of the application on one node, combined with METG(50\%)
measurements, to estimate the strong scalability of
the code:
%% Notably, computing the ideal scaling line requires only
%% the running time on a single node, so the intersection between ideal
%% and ``limit'' can be found with only the single-node time to
%% solution, along with measurements of METG(50\%) at each node
%% count. Using this data it is possible to predict the
%% strong scalability of the code:
i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling} this can be seen as the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

>>>>

One question when considering different programming
systems is: How much overhead does the system add? This question is tricky to answer directly because some systems introduce
overhead \emph{inline} (i.e., by running system internal processes on
the same cores as application tasks), while other systems introduce
overhead \emph{out-of-line} (i.e., by dedicating one or more cores
solely to runtime use). Some systems, like Charm++, PaRSEC, Realm, and Regent,
support both configurations.

@@

We observe that overheads vary by over 5 orders of
magnitude. The most efficient systems are explicitly parallel
and provide very lightweight mechanisms for parallelism. Task-based systems for HPC tend to be next most efficient, and
provide additional features such as automatic dependency discovery and
data movement. Higher overhead systems tend to be designed primarily for
large-scale data analysis or workflows. It is worth
remembering that these are \emph{minimum}
effective task granularities. Applications with an average
task granularity of \emph{at least} this value can usually be expected
to execute efficiently. Typical task granularities will
generally be determined by the application domain being
considered. Most notably, for large-scale data analytics workloads, the higher METG values observed for Spark and
TensorFlow are sufficient. In contrast, for high-performance
scientific simulations, task granularities in the millisecond range
are useful, as such applications communicate (e.g., for halo
exchanges) much more frequently.

@@

There are two points of interest on each ``limit 50\%'' curve: the point
where it intersects ``actual'' and the point where it intersects an
ideal scaling curve, computed by taking the initial time to solution
and assuming linear scaling. These points are marked for Charm++ in
Figure~\ref{fig:strong-scaling} with a black square and black circle,
respectively.
Notably, the ideal-limit intersection (black circle) requires only a
run of the application on one node, combined with METG(50\%)
measurements, to estimate the strong scalability of
the code:
%% Notably, computing the ideal scaling line requires only
%% the running time on a single node, so the intersection between ideal
%% and ``limit'' can be found with only the single-node time to
%% solution, along with measurements of METG(50\%) at each node
%% count. Using this data it is possible to predict the
%% strong scalability of the code:
i.e., the smallest time to solution,
and the number of nodes at which that time is achieved, while
maintaining at least 50\% efficiency. In
Figure~\ref{fig:strong-scaling}, the error in the estimate is the distance
between the black square and circle; these are separated by a factor of
$1.22\times$ in node count, and $1.27\times$ in time to solution.

### 2020-08-24 7_conclusion.tex
Apply Alex's comments.

\begin{itemize}
\item METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.

@@

>>>>

\begin{itemize}
\item Evaluations of programming system performance should avoid using
  TPS or weak scaling to characterize overheads, as these metrics do
  not constrain the useful work achieved. Instead a metric with
  constrained efficiency, such as METG(50\%), is needed to ensure that
  measurements are representative and fair.

\item METG for current distributed programming systems varies by over
  5 orders of magnitude.  Clearly understanding the needed task
  granularity is an important consideration in choosing a programming
  system for a new application.

@@

\item Task-based systems that rely on runtime analysis for the
  discovery of parallelism can suffer from sequential bottlenecks that
  limit scaling. Existing, dynamic task pruning techniques are not
  sufficient to fully mitigate this bottleneck, while static,
  compile-time approaches are able to do so.

### 2020-08-24 e11_metg_predict_strong.tex
Apply Alex's comments.

\vspace{-0.20cm}
\caption{Average factor of separation between limit-ideal and limit-actual intersection across the 4 patterns tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}

>>>>

\vspace{-0.20cm}
\caption{Factor of separation between limit-ideal and limit-actual intersections across all 11 programming systems tested in Section~\ref{subsec:scalability}.\label{tab:metg-predict-strong}}
\vspace{-0.5cm}
\end{table}
